\documentclass[8pt,twocolumn]{jsarticle}

\usepackage[dvipdfmx]{graphicx}

\usepackage{aij-journal-of-technology-and-design}

\bibliography{ref.bib}

\title{全天候型仮設屋根システムの開発}
{DEVELOPMENET OF ALL WEATHERS TEMPORARY ROOF SYSTEM WITH TELESCOPIC SUPPORTS}

\authorA{森口五郎}{Goro MORIGUCHI}{1}
\authorB{矢沢　晋}{Susumu TANIZAWA}{2}
\authorC{木村建治}{Kenji KIMURA}{3}
\authorD{恩村定幸}{Sadayuki ONMURA}{4}

\instituteA{(株)浅沼組技術研究所　所長}
{General Manager, Asanuma Corporation, Technical Research Institute}
\instituteB{(株)浅沼組技術研究所建築工法研究室　室長}
{Head manager, Asanuma Corporation, Technical Research Institute. Constr. Meth. Div.}
\instituteC{(株)浅沼組技術研究所建築工法研究室　課長}
{Manager, Asanuma Corporation, Technical Research Institute. Constr. Meth. Div.}
\instituteD{(株)浅沼組技術研究所建築工法研究室　研究員}
{Engineer, Asanuma Corporation, Technical Research Institute. Constr. Meth. Div.}

\address{〒569-0034　高槻市大塚3-24-1}

\keywords{全天候，仮設屋根，作業環境の改善，伸縮式支柱}
{All weathers, Temporary roof, Improvement of working environment, Telescopic supports}

\abstract{
    All weathers temporary roof system, using three-step telescopic supports roof,was developed to cover workplaces with a roof, and to shelter operations from rain and snow. By carrying out an on site application trial, it was found that because of the protection provided by the system, work could continue even during rain, leading to a considerable increase in productivity. It was also found that the system gave an even greater protection from direct sunlight than was initially anticipated, resulting in an overall improvement of the working environment.
}

\begin{document}
\maketitle
\makefooter

\section{はじめに}
建築工事はその大半が屋外作業となるため，降雨・降雪・炎暑などによって作業効率が低下し，工程の遅延につながるなど，その解決が，昔からの大きな課題とされていた。その解決方法として，天候による影響を受けずに工事を進められる「全天候型仮設屋根システム」が，ここ数年の間に各社で開発され，使用され始めている。

著者らは，これらの既に発表されているシステムとは異なり，断面の異なる３本の柱を内蔵する伸縮式支柱によって屋根を上昇させる独自のシステムを開発し，実際の作業所に適用した。その結果，本システムは機能性，施工性，安全性などに優れ，また屋根によって直射日光が遮断され，作業環境が大幅に改善されることが分かったので，その結果について述べる。
\cite{AutoBuildingSystem}\cite{ParadigmShift}\cite{Kimura1994}

\section{現状分析と開発方針}

\printbibliography[title=参考文献]

\end{document}
